Bayesian Sparsification Methods for Deep Complex-valued Networks

### 2020-04-19 paper/paper.tex
fixed arxiv citations

% motivation and other methods
However, in spite of relative success of $\cplx$-valued networks, compression methods tailored
to $\cplx$-domain remain a niche field of research.
%
Computational efficiency improvement and model compression methods such as quantization
\citep{uhlich_differentiable_2019}, integer-based arithmetic \citep{lin_fixed_2016,chen_fxpnet_2017},
and knowledge distillation \citep{hinton_distilling_2015} appear to be directly applicable
to $\cplx$-valued networks.
%
Certain model sparsification methods, e.g. sparsity inducing regularizers, and magnitude
pruning \citep{zhu_prune_2017}, which reactivates zeroed parameters based on gradients,
can be adapted directly to $\cplx$-valued models. Other methods require additional considerations.
% the more explicitly zero parameters there is, the less computations is needed.

@@

% (sparsity tech large-scale models) gale-elsen-hooker.tex
\citet{gale_state_2019} compare Variational Dropout, magnitude pruning, and $\ell_0$
regularization \citep{louizos_learning_2017} on large-scale models. The latter is a
probabilistic regularization method, which penalizes the expected number of non-zero
entries in $[0, 1]$-valued stochastic parameter masks with learnable hard-concrete
distribution with atoms at $0$ and $1$ \citep{maddison_concrete_2016,jang_categorical_2017}.
Their results suggest that Variational Dropout may achieve good accuracy-sparsity balance
and outperform pruning and $\ell_0$ in deep architectures, although pruning is prefered for
simplicity, stability and speed. They also observe that dropout induces non-uniform sparsity
throughout the model, which \citet{he_amc:_2018} has shown to be essential for superior
compression.
% Magnitude pruning induces user-specified sparsity distributions.
%
% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
% levels of 80\% and up. Variational dropout consistently produces models on-par or better
% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
%

>>>>

% motivation and other methods
However, in spite of relative success of $\cplx$-valued networks, compression methods tailored
to $\cplx$-domain remain a niche field of research.
%
Computational efficiency improvement and model compression methods such as quantization
\citep{uhlich_differentiable_2019}, integer-based arithmetic \citep{lin_fixed_2016,chen_fxpnet_2017},
and knowledge distillation \citep{hinton_distilling_2015} appear to be directly applicable
to $\cplx$-valued networks.
%
Certain model sparsification methods, e.g. sparsity inducing regularizers, and magnitude
pruning \citep{zhu_prune_2018}, which reactivates zeroed parameters based on gradients,
can be adapted directly to $\cplx$-valued models. Other methods require additional considerations.
% the more explicitly zero parameters there is, the less computations is needed.

@@

% (sparsity tech large-scale models) gale-elsen-hooker.tex
\citet{gale_state_2019} compare Variational Dropout, magnitude pruning, and $\ell_0$
regularization \citep{louizos_learning_2018} on large-scale models. The latter is a
probabilistic regularization method, which penalizes the expected number of non-zero
entries in $[0, 1]$-valued stochastic parameter masks with learnable hard-concrete
distribution with atoms at $0$ and $1$ \citep{maddison_concrete_2016,jang_categorical_2017}.
Their results suggest that Variational Dropout may achieve good accuracy-sparsity balance
and outperform pruning and $\ell_0$ in deep architectures, although pruning is prefered for
simplicity, stability and speed. They also observe that dropout induces non-uniform sparsity
throughout the model, which \citet{he_amc:_2018} has shown to be essential for superior
compression.
% Magnitude pruning induces user-specified sparsity distributions.
%
% L0 and dropout work in the low-to-mid sparsity range, variational dropout consistently
% ranked behind L0 on Transformer, and was bested by magnitude pruning for sparsity
% levels of 80\% and up. Variational dropout consistently produces models on-par or better
% than magnitude pruning on ResNet-50, and l0 fails to produce sparse models at all.
%
